Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-01 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
could be also used for nanoinjection of fluorescently labeled molecules into living cells 
\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and dSTORM microscopy, 
and mitochondria, actin and DNA could be successfully stained. One problem with the nanoinjection 
was that artifacts, due to the holes that were introduced into the membranes, could occur 
\cite{Hennig2015_nanoinj}.

>>>>

Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
could be also used for nanoinjection of fluorescently labeled molecules into living cells 
\cite{Hennig2015_nanoinj}. The SICM was therefore combined with wide-field and direct stochastic 
optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
introduced into the membranes, could occur \cite{Hennig2015_nanoinj}.
